---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# `softbib`: Software Bibliographies for `R` Projects

This package detects all the `R` librairies used in a project and automatically creates software bibliographies in PDF, Word, Rmarkdown, and BibTeX formats. Bibliographies can be printed in thousands of styles, using CSL files downloaded from the [Zotero style repository.](https://www.zotero.org/styles)

## Installation

Install the development version of `softbib`:

``` r
library(remotes)
install_github("vincentarelbundock/softbib")
```

## Getting started

Navigate to a project folder, crawl the working directory to get a list of `R` packages, and create bibliographies:

```{r, eval = FALSE}
library(softbib)

setwd("~/path/to/my/R/project/")

softbib()
```

Exclude some packages from the bibliography:

```{r, eval = FALSE}
softbib(exclude = c("base", "dplyr"))
```

Specify the list of packages to include manually:

```{r, eval = FALSE}
softbib(include = c("countrycode", "modelsummary", "marginaleffects"))
```

Download a Citation Style Language file from the Zotero archive and print a bibliography in the style of the American Political Science Review:

```{r, eval = FALSE}
download.file(
  "https://www.zotero.org/styles/american-political-science-review",
  destfile = "apsr.csl")

softbib(style = "apsr.csl")
```

## Ignoring files and folders

`softbib` uses the `renv::dependencies()` function to detect `R` packages used in a project folder. Like the `renv` package, `softbib` can respect user instructions to ignore certain files and folders. To specify those ignore instructions, you must place a file called `.renvignore` in the working directory. This file can include lines such as:

```
ignorethiscript.R
ignorethisfolder/ignorethisscript2.R
ignorethisfolder/
```