---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# `softbib`: Software Bibliographies for `R` Projects

This package detects all the `R` librairies used in a project and automatically creates software bibliographies in PDF, Word, Rmarkdown, and BibTeX formats.

## Installation

You can install the development version of softbib like so:

``` r
library(remotes)
install_github("vincentarelbundock/softbib")
```

## Example

From the terminal, we create a new project with a simple `R` script:

```{sh, eval = FALSE}
mkdir new_project
cd new_project

echo 'library(countrycode)
library(stringr)
countrycode("Canada", "country.name", "iso3c")' > script.R
```

Launch `R`:

```{sh, eval = FALSE}
R
```

Load `softbib` and read the documentation:

```{r, eval = FALSE}
library(softbib)
?softbib
```

Scan the project folder and create software bibliographies:

```{r, eval = FALSE}
softbib()
```
